---
 title: "Google Play Store"
author: "Team ACE"
date: "November 19, 2018"
output: html_document
---

```{r}
require("tidyverse")
require("ggplot2")
```

****Step1: DATA LOADING****

Before loading the data in R. we have manually removed a row having value of $Price='Everyone'. 
This is because, the value of other 2 variables 'App' and 'Category' went missing. It is not possible to predict these values.As a result, the entire row is left shifted, which is making data for each column incorrect.

```{r}
googleplaystore <- read.csv("googleplaystore.csv")
View(googleplaystore)
```
The command above will load the googleplaystore dataset into the 'googleplaystore' dataframe.

****Step2: DATA FILTERING****

***2.1 Identifying NA values***
```{r}
colSums(apply(googleplaystore,2,is.na))
```
The above step will give a count of NA values for each column. 

**** 2.2 Type filtering ****

```{r}
summary(googleplaystore$Type)
```


*******2.3 Price variable filtering *******

#identifying and removing '$' symbol
```{r}
googleplaystore$Price=gsub("\\$","",googleplaystore$Price)
```
#Changing its Type from 'Character' to 'Numeric'
```{r}
typeof(googleplaystore$Price) #before changing
googleplaystore$Price=as.numeric(googleplaystore$Price,na.rm=TRUE)
typeof(googleplaystore$Price) #after change
```
The above command will remove '$' symbol appearing in the value of 'Price'. The type is changed from 'character' to 'double', Now it makes the variable useful for devising descriptive analysis.

```{r}
head(googleplaystore)
```
The above command will display first 6 rows of the frame variable to make sure the data inside $Price is appearing correct or not. 

#Summarising Price

```{r}
summary(googleplaystore$Price) #summary
```


#Performing Descriptive Analysis on Price
```{r}
library(dplyr) #imported library to perform groupby operation
googleplaystore %>%   
  group_by(Category)%>% 
  summarise(Price= mean(Price, na.rm = TRUE))%>%
  arrange(Price)
```
Here, the command is used to to find the mean Price based on the different category.


```{r}
range(googleplaystore$Price,na.rm=TRUE) #range
sd(googleplaystore$Price,na.rm = TRUE) #standard deviation
var(googleplaystore$Price,na.rm = TRUE) #variance
```
The above commands give a decriptive summary of $Price such as variance, standard deviation and range.


**Category and corresponding Rating**
1. **remove NA from Rating based on the category **
**Category vs rating**
```{r}
mean.rating=mean(googleplaystore$Rating,na.rm = TRUE)
googleplaystore[is.na(googleplaystore$Rating),]$Rating = mean.rating
```
The above command will remove NA's from $Rating by replacing it with mean rating.

```{r}
#library(dplyr) #imported library to perform groupby operation
googleplaystore %>%   
  group_by(Category)%>% 
  summarise(Rating= mean(Rating))%>%
  arrange(Rating)

```
The above command will calculate mean rating based on each Category. 


**Category vs Reviews**

```{r}
googleplaystore %>%   
  group_by(Category)%>% 
  summarise(Reviews= mean(Reviews))%>%
  arrange(Reviews)

```

```{r}
library(lubridate)
googleplaystore$Last.Updated <-dmy(googleplaystore$Last.Updated)
typeof(googleplaystore$Last.Updated)
```
The above command will modify LastUpdated to appropriate Date Format.

## CONVERTING INSTALLS

```{r}
googleplaystore$Installs = gsub("\\+", "", as.character(googleplaystore$Installs))
googleplaystore$Installs = as.numeric(gsub(",", "", googleplaystore$Installs))
```
The above command will remove '+' and ',' from $Installs to convert it into numeric datatype. 

```{r}
typeof(googleplaystore$Installs)
```


```{r}
googleplaystore$Size = gsub("M", "", googleplaystore$Size)
googleplaystore$Size = ifelse(grepl("k", googleplaystore$Size), 0, as.numeric(googleplaystore$Size))
```
Here, to remove the variable 'M' which represents Megabyte, we have used the function gsub and also converted into numeric datatype

```{r}
typeof(googleplaystore$Size)
```
The above command will remove 'M' from $Size and will convert it into 'Numeric' datatype.

```{r}
library(dplyr)
googleplaystore %>%
  group_by(Category)%>%
  summarise(category_by_Reviews = mean(Reviews))
```
The above command will provide mean reviews for each Category.
```{r}
library(scales)
ggplot(googleplaystore, aes(x=Reviews, y=Rating)) +
  scale_x_continuous(trans='log10', labels=comma) +
  geom_point(aes(col=Type)) +
  labs(title="Ratings vs Reviews with type") 
  
```
The above plot describes Ratings VS Reviews according to Type Free | Paid

```{r}
library(scales)
ggplot(googleplaystore, aes(x=Installs, y=Rating)) +
  scale_x_continuous(trans='log10', labels=comma) +
  geom_point(aes(col=Type)) +
  labs(title="Ratings vs Installs with type") 
```
The above plot describes Ratings VS Installs according to Type Free | Paid

**Check relationship of SIZE and Installs



```{r}
hist(googleplaystore$Size)
```
The above histogram explains variation in $Size. It is rightly skewed.

```{r}
boxplot(googleplaystore$Size) #check outlyers
```
The above boxplot checks outliers in $Size if any.


```{r}
summary(googleplaystore)
```
The above command displays a Descriptive Summary of the entire DataSet GooglePlayStore.